---
name: Jedidiah Carlson, Ph.D.
position: "Population Genetics | Bioinformatics | Metaresearch"
address: |
         | Seattle, Washington, USA
www: jedidiahcarlson.com
email: "jed [dot] e [dot] carlson [at] gmail [dot] com"
twitter: jedmsp
github: carjed
linkedin: carjed
orcid: "0000-0002-1363-872X"
headcolor: 16690d
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::awesomecv:
always_allow_html: yes
header-includes:
  \usepackage{multicol}
  \usepackage{colortbl}
  \arrayrulecolor{white}
  \usepackage{hhline}
  \definecolor{light-gray}{gray}{0.95}
---

```{r setup, include=FALSE}
library(vitae)
library(ggplot2)
library(dplyr)
library(emojifont)
library(fontawesome)
library(kableExtra)
library(huxtable)
library(gridExtra)
library(tidyverse)
library(googlesheets4)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(gargle_oob_default = TRUE)
```

```{r fetch_data}

cv_data_gs_id <- gs4_find("cv_data", includeTeamDriveItems=TRUE) %>% 
  pull(id)

sheets <- sheet_properties(cv_data_gs_id) %>% pull(name)

cv_data <- set_names(sheets) %>% 
  purrr::map(~sheets_read(cv_data_gs_id, 
                          na="NA", 
                          col_types = c("c"), 
                          sheet = .x))

```
 
\faIcon{briefcase} Professional Experience
============================================

```{r experience}
exp <- rorcid::orcid_employments("0000-0002-1363-872X") %>%
  purrr::map(., purrr::pluck, "affiliation-group", "summaries") %>% 
  purrr::flatten_dfr()

names(exp) <- stringr::str_remove(string = names(exp), pattern = "employment-summary.") 

exp %>%
  mutate(description = 
    "Postdoctoral mentor: Kelley Harris") %>%
  filter(!stringr::str_detect(`role-title`, 'Teaching')) %>% 
  detailed_entries(
    with = `role-title`,
    when = paste(
      paste(`start-date.month.value`,`start-date.year.value`, sep = '/'),
      ifelse(is.na(`end-date`),"Present",paste(`end-date.month.value`,`end-date.year.value`, sep = ', ')),
      sep = ' - '
    ),
    what = paste(`organization.name`, paste0("Department of ", `department-name`), sep = ' — '),
    where = paste(organization.address.city, organization.address.region, sep =', '),
    why = description
    # .protect = FALSE
  )
```

\faIcon{university} Education
==================================

<!-- \protect\faIcon{university} -->
```{r education}

cv_data$education %>%
  detailed_entries(study, dates, university, loc, details, .protect=FALSE)

```

\faIcon*{file} Publications
===========================

```{r pubs}
orcid_pubs <- rorcid::works(rorcid::orcid_id("0000-0002-1363-872X"))  
orcid_titles <- orcid_pubs$title.title.value
orcid_dois <- unlist(lapply(orcid_pubs$`external-ids.external-id`, function(x) x$`external-id-value`[[1]]))

pubs <- scholar::get_publications("4o1Dm1YAAAAJ") %>% 
  dplyr::mutate(author = author %>% 
                  as.character %>% 
                  stringr::str_trim(),
                journal = journal %>% 
                  replace(journal %in% "bioRxiv", "BioRxiv"), 
                first_author = case_when(stringr::str_starts(author, "J Carlson") ~ TRUE,
                                         TRUE ~ FALSE),
                preprint = case_when(tolower(journal)=="biorxiv" ~ TRUE,
                                         TRUE ~ FALSE)) %>% 
  dplyr::filter(!grepl("Mapping the Landscape of Mutation Rate", title)) %>%
  mutate(author=gsub("J Carlson", "\\\\textbf{J Carlson}", author)) %>%
  mutate(author=gsub("[.]{3}", "et al", author)) %>%
  dplyr::arrange(desc(year)) %>%
    mutate(issue=ifelse(str_length(number)>1, paste0(year, ";", number), year)) %>%
  mutate(issue=gsub(" \\(1\\),", ":", issue)) %>%
mutate(issue=gsub(" ", "", issue)) %>%
  mutate(title=tolower(title))

# orcid_pubs_short <- data.frame(title=tolower(orcid_titles), doi=orcid_dois) %>%
#   mutate(doi_http=paste0("https://doi.org/", doi))

# left_join(pubs,
#           orcid_pubs_short,
#           by="title") %>%
#   mutate(title=str_to_title(title)) %>%
#   dplyr::arrange(desc(year)) %>%
#   as_tibble() %>%
#   mutate(journal=gsub("&", "\\\\&", journal)) %>%
#   # mutate(bib="abc") %>%
#   mutate(journal_it=paste0("\\textit{", journal, "}")) %>%
#   rowwise() %>%
#   mutate(bib=paste0(paste(author, title, journal_it, issue, paste0("\\href{", doi_http, "}{[doi:", doi, "]}"), sep=". "), ".")) %>%
#   detailed_entries(
#     #with = title,
#     #what = journal,
#     when = year,
#     # where = year,
#     why = bib,
#     .protect=FALSE)

cr_pubs <- rcrossref::cr_works(dois=orcid_dois)

cr_pubs$data %>%
  mutate(journal=ifelse(grepl("10.1101", doi), "bioRxiv", container.title)) %>%
  # mutate(page=ifelse(is.na(page), page, paste0(""))) %>%
  # mutate(issue=paste0(volume, ";")
  unnest(author) %>% 
  dplyr::filter(!is.na(given)) %>%
  group_by(title, journal, created, url, doi) %>%
  dplyr::slice_head(n=6) %>%
  mutate(given=gsub("[[:lower:][:space:][:punct:]]", "", given)) %>%
  mutate(author=paste0(family, " ", given)) %>%
  summarise(author_list=paste(author, collapse=", ")) %>%
  mutate(author_list=ifelse(str_count(author_list, ",") < 5, author_list, paste0(author_list, ", et al"))) %>%
  mutate(year=substr(created, 1, 4)) %>%
  # dplyr::select(title, journal, year, author_list) %>%
  mutate(author_list=gsub("Carlson J", "\\\\textbf{Carlson J}", author_list)) %>%
  mutate(journal=gsub("&", "\\\\&", journal)) %>%
  mutate(journal_it=paste0("\\textit{", journal, "}")) %>%
  mutate(bib=paste0(paste(author_list, title, journal_it, paste0("(", year, ")"), paste0("\\href{", url, "}{[doi:", doi, "]}"), sep=". "), ".")) %>%
  arrange(desc(created)) %>%
  detailed_entries(
    #with = title,
    #what = journal,
    # when = year,
    #where = year,
    why = bib,
    .protect=FALSE)

```

<!-- \pagebreak -->

\faIcon{dollar-sign} Research Funding
===============================

```{r funding}

cv_data$funding %>%
  detailed_entries(what = source, when = date, with = title, .protect = FALSE)

```

\faIcon{comments} Conferences Presentations and Invited Talks
================================
    
```{r presentations}

cv_data$presentations %>%
  detailed_entries(with = title, what = type, where = location, when = date, .protect=FALSE) 

```

<!-- \pagebreak -->

\faIcon{chalkboard} Teaching Experience
============================================
    
```{r teaching}

cv_data$teaching %>% 
  detailed_entries(with = title, what = type, where = location, when = date, .protect=FALSE)
```

\faIcon{medal} Honors and Awards
===============================

```{r honors}

cv_data$honors %>% 
  detailed_entries(where = loc, what = org, when = date, with = honor, .protect = FALSE)

```

\faIcon{arrows-alt} Service
===============================

```{r service}

cv_data$service %>%
  detailed_entries(with = contrib, what = details, when = date, .protect = FALSE)

```

\faIcon{users} Memberships
===============================

```{r orgs}

cv_data$orgs %>%
  detailed_entries(what = org, when = date, .protect = FALSE)

```

\faIcon{newspaper} Media
==============================

```{r media}


cv_data$media %>%
  detailed_entries(with = title, where = event, when = date, .protect=FALSE)  

```

\faIcon{brain} Skills
================================

```{r skills}

cv_data$skills %>%
  group_by(type) %>%
  summarise(entry = paste(entry, collapse=" — ")) %>%
  detailed_entries(what = entry, with = type, .protect=FALSE)

```
